BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-19 tex/1-intro.tex
Apply Michael's corrections

Among the challenges in developing a blog archiving software is the design of a web crawler capable of efficiently traversing blogs to harvest their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further narrowed by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.

>>>>

Among the challenges in developing a blog archiving software application is the design of a web crawler capable of efficiently traversing blogs to harvest their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further narrowed by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.

### 2014-01-19 tex/2-algorithms.tex
Apply Michael's corrections

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable to all blog posts. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\alph*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
\end{enumerate}
Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.

@@

\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

>>>>

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for extracting authors, dates and comments. Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable throughout a blog. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\alph*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
\end{enumerate}
Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.

@@

\begin{itemize}
  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

### 2014-01-19 tex/3-architecture.tex
Apply Michael's corrections

This section provides an overview \TODO{issue with subsection name} of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

@@

Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether an URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice among web developers.

@@

The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

>>>>

This section provides an overview of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

@@

Given a URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether an URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice among web developers.

@@

The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for an estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

### 2014-01-19 tex/4-evaluation.tex
Apply Michael's corrections

Our evaluation is articulated in two parts. First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting article and title from web pages. The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time. Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code. Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.

@@

On our test dataset \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page. On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules. Therefore, results showed in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.

>>>>

Our evaluation is articulated in two parts. First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting articles and titles from web pages. The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time. Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code. Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.

@@

On our test dataset, \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page. On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules. Therefore, results shown in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as evidence that our approach is more suitable when working with blogs.
